---
title: "Lab03 - wrapping up t tests and confidence intervals for ANOVA"
author: "Your Name Here"
output: pdf_document
---

## Goals

The goal in this lab is to understand:

1. how the output from the `fit.contrast` function relates to all the formulas we discussed on Friday
2. how those results are used to find the t statistic for a hypothesis test
3. how those results are used to find a confidence interval

## Loading packages

Here are some packages with functionality you may need for this lab.  Run this code chunk now.

```{r}
library(readr)
library(dplyr)
library(ggplot2)
library(gridExtra)
library(mosaic)
library(gmodels)

options("pillar.sigfig" = 10) # print 10 significant digits in summarize output
```

## Example Study (Case Study 6.1.1 in Sleuth 3, description excerpted from the book)

A 1990 study conducted a randomized experiment to explore how physical handicaps affect people's perception of employment qualifications.  The researchers prepared five videotaped job interviews using the same two male actors for each.  A set script was designed to reflect an interview with an applicant of average qualifications.  The videos differed only in that the applicant appeared with a different handicap:

 1. in one, he appeared to have no handicap;
 2. in a second, he appeared to have one leg amputated;
 3. in a third, he appeared on crutches;
 4. in a fourth, he appeared to have impaired hearing;
 5. and in a fifth, he appeared in a wheelchair.

Seventy undergraduate students from a US university were randomly assigned to view the videos, fourteen to each video.  After viewing ther video, each subject rated the qualifications of the applicant on a 0 to 10 point applicant qualification scale.

The following R code reads in a data set with the results.  By setting the levels of the Handicap variable in this data set, I have told R to use the ordering of the groups outlined above instead of alphabetic order.

```{r}
handicaps <- read_csv("http://www.evanlray.com/data/sleuth3/ex0601_handicaps.csv") %>%
  mutate(
    Handicap = factor(Handicap, levels = c("None", "Amputee", "Crutches", "Hearing", "Wheelchair"))
  )

dim(handicaps)
head(handicaps)
```

## 1. Exploration of sample data

#### (a) Plot

Use the space below to make a plot comparing applicant qualification scores for the different handicaps.  (No need to make every possible plot, one will do.)

```{r}

```

#### (b) Sample means in each group

Use the space below to find the sample mean score for each handicap.

```{r}

```

## 2. Hypothesis test set up

Suppose we want to conduct a test of whether or not the average qualification score when the applicant appears to have a hearing impairment is the same as or different than the average qualification score when the applicant is using an assistive device for mobility (crutches or a wheelchair).  Express the null and alternative hypotheses for the test as a linear combination of the means $\mu_1$ through $\mu_5$.  What are the coefficients for each mean?

Note: our book uses the symbol $\gamma$ (gamma) to represent this combination of population means; we can think of this as a parameter to estimate.




## 3. Conduct the hypothesis test and confidence interval calculations using `lm` and `fit.contrast`

Use the `fit.contrast` function in R to estimate $\gamma$, obtain a p-value for the test you set up in part (a), and find a 95% confidence interval for $\gamma$.  (Here, your argument should be the actual level of the confidence interval that you want to calculate, 0.95 in this case.)

```{r}
anova_fit <- lm(Score ~ Handicap, data = handicaps)
fit.contrast(anova_fit, "Handicap", c(0, 0.5, -1, 0, 0.5), conf.int = 0.95)
```

## 4. Verify estimate

We estimate $\gamma$ (a linear combination of "population" means) with the corresponding linear combination of sample means.  This estimate is referred to as $g$ in our textbook.  Using your results from 1 (b), verify that the estimate calculated by `fit.contrast` in part 3 makes sense.



## 5. Verify calculation of t statistic

The general form of a t statistic is

$$\frac{\text{Estimate} - \text{Parameter Value from Null Hypothesis}}{\text{SE(Estimate)}}$$

In this case, that works out to

$$\frac{g - \gamma^{null}}{SE(g)}$$

$SE(g)$ is the standard error of $g$: an estimate of the variability of the statistic $g$ across all possible samples.  This standard error is calculated using the formula we discussed last time, $SE(g) = s_{pooled}\sqrt{\frac{C_1^2}{n_1} + \cdots + \frac{C_I^2}{n_I}}$.  We don't need to reproduce that calculation; we will just let the computer do that and make sure we understand how it is used for confidence intervals and hypothesis tests.

Taking $SE(g)$ as given in the output from `fit.contrast`, verify that the t statistic shown in that output is correct.  What are the degrees of freedom for the t statistic?



## 6. Verify calculation of p-value.

The p-value for the test is calculated as the probability of obtaining a t statistic at least as extreme as the value calculated in part 5.  We can use the `pt` function in R to calculate this probability as in the handout.



## 7. Verify calculation of confidence interval.

The generic formula for a confidence interval is

$$[Estimate - t^* SE(Estimate), Estimate + t^* SE(Estimate)]$$

Using appropriate output from `qt` as well as the estimate and the standard error of the estimate as given in the output from `fit.contrast`, verify the confidence interval bounds given in the output from `fit.contrast`.


